---
output: rmarkdown::github_document
---

`jerichojars` : Java Archive Wrapper Supporting the 'jericho' Package

Contents of the 'Jericho HTML Parser' Java archive by Martin Jericho <http://jericho.htmlparser.net/docs/index.html> provided to support functions in the 'jericho' package.

As a result of using a Java library, this package requires `rJava`.

While the main intent is to use this with `jericho`, you can use it out of the box as-is (see below and the [javadocs](http://jericho.htmlparser.net/docs/javadoc/index.html)).

NOTE: Package version # reflects the version # of the included JAR file.

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/jerichojars")
```

```{r message=FALSE, error=FALSE, warning=FALSE}
library(jerichojars)
library(tidyverse)

c(
  "https://medium.com/starts-with-a-bang/science-knows-if-a-nation-is-testing-nuclear-bombs-ec5db88f4526",
  "https://en.wikipedia.org/wiki/Timeline_of_antisemitism",
  "http://www.healthsecuritysolutions.com/2017/09/04/watch-out-more-ransomware-attacks-incoming/",
  "http://rud.is/b/"
) -> urls

map_chr(urls, ~paste0(read_lines(.x), collapse="\n")) -> sites_html

map(sites_html, ~{
  
  b <- new(J("net.htmlparser.jericho.Source"), .x)
  
  b$getAllElements("a") %>% 
    as.list() %>% 
    map(~.x$getAttributeValue("href")) %>% 
    flatten_chr()
  
}) 
```